---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# state

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/state)](https://CRAN.R-project.org/package=state)
[![R-CMD-check](https://github.com/calderonsamuel/state/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/calderonsamuel/state/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/calderonsamuel/state/graph/badge.svg)](https://app.codecov.io/gh/calderonsamuel/state)
<!-- badges: end -->

The goal of state is to provide an alternative to `shiny::reactiveValues()` that includes type safety functionality. Create a type safe reactiveValues with `state_manager()` and initialize values with `state()`, where the first argument is the initial value and the second one is the expected S7 class. 

## Installation

You can install the development version of state like so:

```{r eval=FALSE}
pak::pak("calderonsamuel/state")
```


## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(state)
```

Create a state manager

```{r}
sm <- state_manager()
```

Initialize some state

```{r}
sm$counter <- state(0L, S7::class_integer)
```

It will error if you try to assign a different type

```{r, error=TRUE}
sm$counter <- "new value"
```

Or if you try to initialize state without using `state()`

```{r, error=TRUE}
sm$new <- 0L
```


It will work if you assign a value of the expected class

```{r}
sm$counter <- 1L
```

You can use it as a typical reactiveValues object

```{r}
shiny::isolate(sm$counter)
```

You can also use key S3 classes provided by the base packages

```{r}
sm$df <- state(mtcars, S7::class_data.frame)
sm$date <- state(as.Date("2025-01-01"), S7::class_Date)
```

Or provide your custom S7 classes

```{r}
animal <- S7::new_class(
  name = "animal",
  properties = list(
    n_legs = S7::class_integer
  )
)

bird <- animal(n_legs = 2L)
dog <- animal(n_legs = 4L)

sm$my_animal <- state(bird, animal)
sm$my_animal <- dog
shiny::isolate(sm$my_animal)
```



